Measurement Bias from Address Aliasing

### 2014-05-25 paper.tex
Fix width of heap table

% Table with detailed performance data, use estimated for O2 because it does not need as many columns (!)
\begin{table}[t]
  %\renewcommand{\tabcolsep}{3pt} % Less padding between cells
  \tbl{Most interesting performance counters and correlation with cycle count for optimization O2, estimated cost accounting for constant overhead.\label{tab:convstats}}{
    \pgfplotstabletypeset[
      %font=\footnotesize,
      int detect, % Output whole numbers for counter values
      col sep=comma,
      columns={Performance counter, Correlation, 0, 2, 4, 8},
      column type=r,
      columns/Performance counter/.style={
        string type, 
        column type=l,
        column type/.add={|}{},
        postproc cell content/.append code={
          \pgfkeysalso{@cell content=\perfctr{##1}}
        }
      },
      columns/Correlation/.style={
        fixed,
        fixed zerofill,
        precision=2
      },
      every head row/.style={
        output empty row,
        before row={\hline
          Performance counter & $r$ & 0 & 2 & 4 & 8 \\
        },
        after row=\hline\hline
      },
      every last row/.style={after row=\hline},
      every last column/.style={column type/.add={}{|}}
    ]{bin/conv-default-o2.estimate.csv}
  }
\end{table}

>>>>

% Table with detailed performance data, use estimated for O2 because it does not need as many columns (!)
\begin{table}[t]
  \renewcommand{\tabcolsep}{3pt} % Less padding between cells
  \tbl{Relevant performance counters and correlation ($r$) with cycle count for optimization O2. Estimated cost accounting for constant overhead.\label{tab:convstats}}{
    \pgfplotstabletypeset[
      int detect, % Output whole numbers for counter values
      col sep=comma,
      columns={Performance counter, Correlation, 0, 2, 4, 8},
      column type=r,
      columns/Performance counter/.style={
        string type, 
        column type=l,
        column type/.add={|}{},
        postproc cell content/.append code={
          \pgfkeysalso{@cell content=\perfctr{##1}}
        }
      },
      columns/Correlation/.style={
        fixed,
        fixed zerofill,
        precision=2
      },
      every head row/.style={
        output empty row,
        before row={\hline
          Performance counter & $r$ & 0 & 2 & 4 & 8 \\
        },
        after row=\hline\hline
      },
      every last row/.style={after row=\hline},
      every last column/.style={column type/.add={}{|}}
    ]{bin/conv-default-o2.estimate.csv}
  }
\end{table}
